### 2016-07-26 notions.tex
cheers
slight change to correctness experiment

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpCorrect{\setprim,\distr{\calS}{},r}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$\mathrm{err}\gets 0$\\
$(M,\aux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\aux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$a$
}
}
\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
  the target multiset~$S$ is sampled from~$\calS$ according to distribution~$\distr{\calS}{}$.} 
\label{fig:correctness}
\end{figure}

@@

\heading{Relationships among notions.}
\tsnote{Seems that correctness and privacy are orthogonal?  Not sure about relationship between different notions of privacy.}
\tsnote{Not even clear how to reduce correctness to the stronger version of one-wayness.  In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the stronger version of one-wayness, the adversary expects~$(M,\aux)$ as input.}
\tsnote{Reducing correctness to the weaker version is syntactically possible, but not clear how to connect the success events.  In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?  Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.  Then the correctness attacker does what?  Ask some query~$q_z$ related to~$z$ (remember, queries are not syntactically restricted to set membership!) and see if the oracle returns the true value $q_z(S)$?  This is pretty complicated... Note that any query~$q$ the one-wayness adversary asks can be checked locally against the true value~$q(S)$ by the correctness adversary.  But still, it's not clear how to do a quality reduction.  }
\tsnote{Likewise the other way: the one-wayness adversary does not get~$S$, and yet needs to provide this to the correctness adversary.}

>>>>

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpCorrect{\setprim,\distr{\calS}{},r}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$\mathrm{err}\gets 0$\\
$(M,\aux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\aux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
  the target multiset~$S$ is sampled from~$\calS$ according to distribution~$\distr{\calS}{}$.} 
\label{fig:correctness}
\end{figure}

@@

\heading{Relationships among notions.}
If we allow for trivial schemes, e.g. $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.\tsnote{In general, it isn't clear how to reduce correctness to the Priv notion.  In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the adversary expects~$(M,\aux)$ as input.}
Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).
\tsnote{Reducing correctness to the weaker version, wPriv, is syntactically possible, but not clear how to connect the success events.  In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?  Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.  Then the correctness attacker does what?  Ask some query~$q_z$ related to~$z$ (remember, queries are not syntactically restricted to set membership!) and see if the oracle returns the true value $q_z(S)$?  This is pretty complicated... Note that any query~$q$ the one-wayness adversary asks can be checked locally against the true value~$q(S)$ by the correctness adversary.  But still, it's not clear how to do a quality reduction.  }

\tsnote{Likewise the other way: the one-wayness adversary does not get~$S$, and yet needs to provide this to the correctness adversary.}
